Analysis paper

### 2021-03-26 analysis/analysis.Rmd
add some interpretation

-[x] create plots
-[x] combine plots into one
-[ ] shade dates that are excluded in scores
-[ ] maybe add density plot on the y axis
-[ ] maybe use mean scores ratio instead of WIS for plot with score over time

@@

@@

### same plot with mean score ratio
not sure why there is a whole in the plot...
```{r}
scores_target_forecastdate  %>%
  ggplot(aes(x = as.Date(forecast_date), y = scaled_rel_skill, colour = model)) + 
  geom_line() + 
  geom_point() + 
  theme_light() + 
  facet_grid(target_type ~ location_name, scales = "free") +
  theme(legend.position = "bottom") +
  labs(y = "mean score ratio", x = "date") 
```

>>>>

- [x] create plots
- [x] combine plots into one
- [ ] shade dates that are excluded in scores
- [ ] maybe add density plot on the y axis
- [ ] maybe use mean scores ratio instead of WIS for plot with score over time

@@

```
**What we learn from this plot**
- severe overshooting for Renewal model
- need to increase value for position dodge
- reporting artifacts around christmas

@@

**What we learn from this plot**
- all models perform terribly around Christmas
- the effect is much stronger in Germany than in Poland
- these artifacts around Christmas hit Renewal hardest
- in Germany scores are high in the beginning and the end, but it doesn't seem to correlate perfectly with the absolute value of the number of weekly cases

**Further things we could look at**
- maybe look at correlation between the number of weekly cases and the score?
- look at scores for rising and falling parts of the epidemic separately

### same plot with mean score ratio
```{r}
scores_target_forecastdate  %>%
  ggplot(aes(x = as.Date(forecast_date), y = scaled_rel_skill, colour = model)) + 
  geom_line() + 
  geom_point() + 
  theme_light() + 
  facet_grid(target_type ~ location_name, scales = "free") +
  theme(legend.position = "bottom") +
  labs(y = "mean score ratio", x = "date") 
```

**What we learn from this plot**
- There is a gap in the plot where there shouldn't be a gap. Nikos is a bad Padawan and needs to look at this again. Need to think a minute about what we actually see here. It is not exactly the WIS of one model over the WIS of the baseline, but something slightly different
- In German cases there are two spikes that I think would be interesting to look at
- death forecasts look quite a lot messier than case forecasts
